---
title: "Lookup challenge"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---


I have a `data_df` that has a some incorrect `id`s for certain values.

I have a `lookup_df` that has the correct `id`s for those values.

I want to create a new `data_df$id_fixed` column that corrects the `id` (i.e. uses `lookup_df$id`) when `data_df$value` matches one in `lookup_df$value`, but keep the old `data_df$id` if the value does not match.

Complicating factors of note: `data_df` is 1.5M obs. with 170 variables.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(reprex)
```

```{r create_dfs}
# lookup_df
id = c("01", "02")
value = c("a", "b")
lookup_df = data.frame(id, value)

# data_df
id = c("04", "04", "01", "05", "05", "02", "06", "07")
value = c("a", "a", "a", "b", "b", "b", "c", "d")
data_df = data.frame(id, value)
```

```{r peek}
lookup_df
data_df
```

My inclination was to use a case_when to look forthe value is in the `lookup_df`, then replace the `id` with the matching `lookup_df$id`. I can find the matches ...

```{r lookup_try}
data_df %>%   
  mutate(
    id_new = case_when(
      value %in% lookup_df$value ~ "fixit",
      TRUE ~ id
    )
  )
```

... but I don't know how to replace the value with the matching `lookup_df$id`. If I use `lookup_df$id` on the right side of the case_when equation, then I think it returns ALL the `lookup_df$id`s, not just the one from the matching row.

```text
data_df %>%   
  mutate(
    id_new = case_when(
      value %in% lookup_df$value ~ lookup_df$id,
      TRUE ~ id
    )
  )
```

The error is:

"Error: Problem with `mutate()` input `id_new`. x `value %in% lookup_df$value ~ lookup_df$id` must be length 8 or one, not 2. ℹ Input `id_new` is `case_when(value %in% lookup_df$value ~ lookup_df$id, TRUE ~ id)`."

